Seniority and hierarchy configuration interaction for radicals and excited states

### 2023-08-14 Manuscript/manuscript.tex
correction
fix ref

For a reference containing unpaired electrons, an approximate CI model will generally produce spin-contaminated states.
One can impose the solutions to have well-defined spin by including additional determinants generated via higher-order hierarchy, which account for the missing spin-flip configurations.
The spin-contamination problem and its solution are therefore equivalent to that encountered in eCI. \cite{Maurice_1996}
Here, we have employed this procedure and considered pure spin states.
For the $s_0 = 2$ reference, one could alternatively employ a high-spin triplet determinant (two unpaired spin-up electrons), 
rather than the low-spin determinant shown in Fig.~\ref{fig:ref}.
Regardless of the choice, hCI (as eCI) produces the same energies for the triplet states, provided that a spin eigenstate is imposed for the low-spin reference.

>>>>

For a reference containing unpaired electrons, an approximate CI model will generally produce spin-contaminated states.
One can impose the solutions to have well-defined spin by including additional determinants generated via higher-order hierarchy, which account for the missing spin-flip configurations.
The spin-contamination problem and its solution are therefore equivalent to that encountered in eCI. \cite{Maurice_1996}
Here, we have employed this procedure and considered pure spin states.
For the $s_0 = 2$ reference, one could alternatively employ a high-spin triplet determinant (two unpaired spin-up electrons), 
rather than the low-spin determinant shown in Fig.~\ref{fig:hCI}.
Regardless of the choice, hCI (as eCI) produces the same energies for the triplet states, provided that a spin eigenstate is imposed.
